Assessing Power of the California Microhap Baseline for GSI (and calculating Fst)

### 2024-11-06 002-GSI_and_Fst.Rmd
Change a footnote reference in Table 1

# and now do some formatting
fbmet5 <- fbmet4 %>%
  ungroup() %>%
  mutate(
    `Sampling Months` = sprintf("\\raisebox{-0.12 em}{\\includegraphics[height=1.02em]{../%s}}", sparkline_path),
    `Year Range` = sprintf("%d--%d", min_year, max_year)
  ) %>%
  select(`Mainstem River`, abbrv, map_text, run_timing_for_table, repunit, ESU, N, N_date, `Sampling Months`, `Year Range`) %>%
  mutate(map_text = str_replace(map_text, ",.*$", "")) %>% # this removes the abbreviations after the commas on the map names
  mutate(N_date = replace_na(N_date, 0L)) %>%
  rename(
    `Mainstem River$^1$` = `Mainstem River`,
    Code = abbrv,
    `Location Name$^2$` = map_text,
    Run = run_timing_for_table,
    `Reporting Unit$^4$` = repunit,
    `ESU$^4$` = ESU,
    `$N$` = N,
    `$N_\\mathrm{day}^5$` = N_date
  ) %>%
  arrange(factor(Code, levels = collection_order))

>>>>

# and now do some formatting
fbmet5 <- fbmet4 %>%
  ungroup() %>%
  mutate(
    `Sampling Months` = sprintf("\\raisebox{-0.12 em}{\\includegraphics[height=1.02em]{../%s}}", sparkline_path),
    `Year Range` = sprintf("%d--%d", min_year, max_year)
  ) %>%
  select(`Mainstem River`, abbrv, map_text, run_timing_for_table, repunit, ESU, N, N_date, `Sampling Months`, `Year Range`) %>%
  mutate(map_text = str_replace(map_text, ",.*$", "")) %>% # this removes the abbreviations after the commas on the map names
  mutate(N_date = replace_na(N_date, 0L)) %>%
  rename(
    `Mainstem River$^1$` = `Mainstem River`,
    Code = abbrv,
    `Location Name$^2$` = map_text,
    Run = run_timing_for_table,
    `Reporting Unit$^3$` = repunit,
    `ESU$^4$` = ESU,
    `$N$` = N,
    `$N_\\mathrm{day}^5$` = N_date
  ) %>%
  arrange(factor(Code, levels = collection_order))
